---
title: "Assignment 3 Code"
author: "Emil Vedvik, Magnus C. Ørke, Oskar H. Simensen"
date: "1 april 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
library(FrF2)
library(nortest)
```

In this paper, we use a full factorial $2^3$ design to determine the effect of color, distance and throwing arm on a persons ability to throw a round object in a bucket.

Ball play is an integral part of growing up in the modern world. A common perception among human beings is that we are subject to handedness; the distinction between one dominant hand, and one less capable, less valued, non-dominant hand. Upon this assumption we live out our lives, not concerned about the correctnes of our worldviews and assumptions.

We expect the throwing arm and distance to both have effects on accuracy, and it seems plausible that they would have an interaction effect. Speaking from past experience, one's ability to throw precisely is much more difficult 


In order to assess the accuracy of the person throwing, we chose the number of 




#################################################
Implementation of the experiment:
- Randomization.
- Describe any problems with the implementation (maybe the randomization was not    followed?).
- Is each experiments a genuine run replicate, that is reflects the total           variability of the experiment? (Each trial should be a performed independently    and constitute a full trial.)
###################################################################
The experiment were conducted as a 




```{r}
#color: blue=-1,red=1
#arm: right=-1, left=1
#distance: near=-1, far=1

# c<-matrix(c(1,1,1,1,1,1,1,
#             1,-1,1,-1,1,-1,-1,
#             1,1,-1,1,-1,-1,-1,
#             1,-1,-1,-1,-1,1,1,
#             -1,-1,1,1,-1,-1,1,
#             -1,1,1,-1,-1,1,-1,
#             -1,-1,-1,1,1,1,-1,
#             -1,1,-1,-1,1,-1,1),byrow=TRUE,nrow=8)
# c <- cbind(rbind(c,c,c,c),0.1*c(5,3,1,2,1,5,2,0,2,4,2,2,7,6,1,3,6,5,2,4,7,6,1,5,4,5,6,3,7,8,0,2))
# colnames(c) <- c("color","arm","distance","color.arm","color.distance","arm.distance","color.arm.distance","hitrate")
# df <- as.data.frame(c)
# linreg <- lm(formula=hitrate~.,data=df)
# summary(linreg)
# model.matrix(linreg)

# plot(linreg)
# MEPlot(linreg)
# cubePlot(linreg,"color","arm","distance","color.arm","color.distance","arm.distance","color.arm.distance")
# IAPlot(linreg)

hitrate <- 0.1*c(1,0,2,1,5,2,3,5,6,2,4,1,2,3,2,7,6,1,2,4,7,6,5,5,6,2,4,5,3,7,8,0)
obs <- FrF2(nruns=8,nfactors=3,randomize=TRUE,factor.names=c("arm","distance","color"),replications=4,seed=1)
obs
obs <- add.response(obs,hitrate)
linreg2 <- lm(hitrate~(arm+distance+color)^3,data=obs)
summary(linreg2)
MEPlot(linreg2)
IAPlot(linreg2)
DanielPlot(linreg2)

rsiduals <- rstudent(linreg2)
plot(linreg2$fitted,rsiduals)

qqnorm(rsiduals)
qqline(rsiduals)
ad.test(rstudent(linreg2))
obs[,"hitrate"] <- obs[,"hitrate"]+0.0001 #boxcox demands values of response>0
linreg2.mod <- lm(hitrate~(arm+distance+color)^3,data=obs)
summary(linreg2.mod)
boxcox(linreg2,plotit=TRUE)
```



